Group 1: Tennis 

### 2019-12-11 Group1Prez.Rmd
Updated slides and added a slide about info on data used

- Where Probability A loses a rally given A served:$$q_A^R = 1-\frac{\text{Points Won On Serve}}{\text{Points Served}}$$

@@

- $$p_A^S=\text{Probabilty A wins a set given A served}$$

- $$p_B^S=\text{Probabilty B wins a set given B served}$$

>>>>

- Where Probability A loses a rally given A served: 
$$q_A^R = 1-\frac{\text{Points Won On Serve}}{\text{Points Served}}$$

@@

- $p_A^S=\text{Probabilty A wins a set given A served}$

- $p_B^S=\text{Probabilty B wins a set given B served}$

## Data being used 
Data used in paper:

  - Men and Women semifinalists in the 2002 U.S Open tournament

  - Men and Women semifinalists in the 2002 Wimbledon tournament

Data used in our simulation:

  - Men and Women semifinalists in the 2019 Wibledon tournament
